\documentclass[char]{FateDarkDawn}
\begin{document}
\name{\cChurch{}}

You are the representative from the Catholic Church selected for the challenging task of overseeing this Sixth Holy Grail War. You are also a member of the Executors -- an elite branch of the Church tasked with destroying heretics and protecting civilians from the dark things in the world they cannot protect themselves from. You have been in Fuyuki City, Japan for the last 2 years, making the necessary preparations. This is not a very prestigious appointment, but proper execution of your tasks will ensure that you are cycled out of here and back to the Vatican sooner rather than later.

As the arbiter, you know a little about the competitors in this war -- namely who are all the mages participating and which class of servant is paired with which mage. As a supposedly neutral party, you should be able to convince people to share information with you, some of which you need for yourself, some of which you will want for trading with others. You are encouraged to convince people to take you into their confidence as much as possible.

The church has a number of interests in the events of these wars, despite the fact that this grail is not \emph{\iGrail{\MYname}}. The first and foremost of these is to ensure that the mages do not substantially upset the balance of this world. Many mages desire \iGrail{\MYname} for massive worldly wishes like excessive money or power. These would quickly destroy the carefully cultured world that the Church has maintained for thousands of years. A few mages lack worldly desires, and these oddities should be encouraged. If a mage should happen to want something small and personal, like skill in art, or something entirely outside the scope of the world, like access to ``The Root'' (The root of all magic, and the original intention of the ritual that became the Holy Grail War), they are particularly good candidates for your support. Of course the church is publicly neutral and you must endeavor to not get caught. Still, when push comes to shove, saving the world from power-hungry mages is more important than maintaining the church's neutrality.

Secondly, as an Executor, you must protect the citizens of Fuyuki City from the deadly conflict occurring in their midst. This includes any masters who have forfeited their status as masters (by using up all of their \iCommand{}). Masters may request your help in covering up situations where a battle lasted to long, or started too early and civilians witnessed it. In these cases, you must employ your ``\aForget{}'' ability. You should also not hesitate to bring to bear the full strength of your defensive abilities to protect masters who have forfeited their status. After all, wanton killing is not something the church condones.

Thirdly, as the arbiter of the war, you are tasked with recovering any unspent \iCommand{\MYname}s. If a master is killed, you may use your ``\aRetrieveCommand{}'' ability to retrieve unspent \iCommand{\MYname}s and transfer them to yourself. It is not out of the realm of possibility that the Caster class servant or a particularly powerful mage to have the ability to steal \iCommand{\MYname}s and use them to do unusual things like compel servants not sworn to them to perform specific actions. To head off any such re-imagining of the rules, the arbiter is tasked with retrieving \iCommand{\MYname}s. You can also use this ability to give out \iCommand{\MYname}s, although you should do so only \emph{very} sparingly (on the scale of defeating an extra-dimensional monster that randomly appears to terrorizes the city.)

Lastly, hopefully it goes without saying that if you don't survive the war, you won't be around to get that promotion and get out of here.

\begin{itemz}[Goals]
	\item Figure out what each master and servant wants from the Grail, and decide who you should support. Then do so without being caught doing so.
	\item Protect any Masters who lose their servants. The church does \emph{not} condone unnecessary killing.
	\item Protect civilians and cover up any mage activity that impacts civilians.
	\item Recover any unspent command seals.
	\item Survive the war.
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cBarth{}} A mage paired to Rider.
	\contact{\cEizen{}} A mage paired to Saber.
	\contact{\cMatou{}} A mage paired to Assassin.
	\contact{\cFaolan{}} A mage paired to Lancer.
	\contact{\cSophia{}} A mage paired to Archer.
	\contact{\cTohsaka{}} A mage paired to Berserker
	\contact{\cVelvet{}} A mage paired to Caster.
\end{contacts}

\end{document}
